Supporting information

### 2023-11-01 paper/supporting_information.qmd
add reference
keep supporting tex

---
title: Supporting information
bibliography: bibliography.bib
number-sections: true
format:
  html:
    embed-resources: true
    include-in-header: mathjax.html
  pdf: default
  docx: default
---

>>>>

---
title: Supporting information
bibliography: bibliography.bib
number-sections: true
format:
  html:
    embed-resources: true
    include-in-header: mathjax.html
  pdf: 
    keep-tex: true
  docx: default
---
